---
title: "Resume Experiment"
format: html
execute: 
  echo: false
---


```{r}
#| message: false

library(tidyverse)
library(tidymodels)
library(broom)
library(marginaleffects)
library(easystats)

x <- read_csv("https://raw.githubusercontent.com/PPBDS/bootcamp/refs/heads/master/_internal/data/resume.csv",
        show_col_types = FALSE) |>
  mutate(call = as.factor(call))

```


```{r}
logistic_reg() |> 
    fit(as.factor(call) ~ city + quality, data = x)
```


```{r}
logistic_reg() |> 
    fit(as.factor(call) ~ city + quality, data = x)
```

```{r}

logistic_reg() |>
  fit(call ~ ethnicity + gender, data = x) |>
  tidy(conf.int = TRUE, exponentiate = TRUE)

```

```{r}
logistic_reg() |>
  fit(call ~ ethnicity + city, data = x) |>
  tidy(conf.int = TRUE, exponentiate = TRUE)

```

```{r}
logistic_reg() |>
  fit(call ~ ethnicity + jobs, data = x) |>
  tidy(conf.int = TRUE, exponentiate = TRUE)

```

```{r}
logistic_reg() |>
  fit(call ~ ethnicity + experience, data = x) |>
  tidy(conf.int = TRUE, exponentiate = TRUE)

```


```{r}
logistic_reg() |>
  fit(call ~ ethnicity + honors, data = x) |>
  tidy(conf.int = TRUE, exponentiate = TRUE)

```

```{r}
logistic_reg() |>
  fit(call ~ ethnicity + holes, data = x) |>
  tidy(conf.int = TRUE, exponentiate = TRUE)

```


```{r}
logistic_reg() |>
  fit(call ~ ethnicity + special, data = x) |>
  tidy(conf.int = TRUE, exponentiate = TRUE)

```

```{r}

logistic_reg() |> 
  fit(as.factor(call) ~ ethnicity + quality + gender + name + city + jobs + experience + honors + holes + special, data = x) |> 
  tidy(conf.int = TRUE, exponentiate = TRUE, digits = 2) |> 
  select(term, estimate, conf.low, conf.high)

```

\documentclass{article}
\usepackage{amsmath}
\begin{document}

\section*{Logistic Regression Model}

Let \( Y_i \in \{0, 1\} \) denote whether applicant \( i \) received a callback.

\subsection*{Model Specification}

\[
\log \left( \frac{P(Y_i = 1)}{1 - P(Y_i = 1)} \right) = \beta_0 
+ \beta_1 \cdot \text{eth}_i 
+ \beta_2 \cdot \text{qual}_i 
+ \beta_3 \cdot \text{gender}_i 
+ \beta_4 \cdot \text{name}_i 
+ \beta_5 \cdot \text{city}_i 
+ \beta_6 \cdot \text{jobs}_i 
+ \beta_7 \cdot \text{exp}_i 
+ \beta_8 \cdot \text{hon}_i 
+ \beta_9 \cdot \text{holes}_i 
+ \beta_{10} \cdot \text{special}_i
\]

\subsection*{Probability Form}

\[
P(Y_i = 1) = \frac{1}{1 + \exp\left( 
- \left(
\beta_0 
+ \beta_1 \cdot \text{eth}_i 
+ \beta_2 \cdot \text{qual}_i 
+ \beta_3 \cdot \text{gender}_i 
+ \beta_4 \cdot \text{name}_i 
+ \beta_5 \cdot \text{city}_i 
+ \beta_6 \cdot \text{jobs}_i 
+ \beta_7 \cdot \text{exp}_i 
+ \beta_8 \cdot \text{hon}_i 
+ \beta_9 \cdot \text{holes}_i 
+ \beta_{10} \cdot \text{special}_i
\right)
\right)}
\]

\end{document}


<!-- name indicates applicant's first name.

gender indicates gender.

ethnicity indicates ethnicity (i.e., Caucasian-sounding vs. African-American sounding first name).

quality indicatesquality of resume.

call indicates whether the applicant was called back?

city indicates city: Boston or Chicago.

jobs indicates number of jobs listed on resume.

experience indicates number of years of work experience on the resume.

honors: Did the resume mention some honors?

holes: Does the resume have some employment holes?

special: Does the resume mention some special skills? -->